Geospatial - Assignment 1 - Moritz Peist, Noemi Lucchi, Simon Vellin

### 2025-01-27 hw1/submission_notebook.Rmd
adding plot from authors
adding comment about the censobr package

@@

In comparison the third paper map looked as follows: ![Figure x]()

>>>>

Additionally, we explored the R package censobr, which is expected to contain Brazil's census data for earlier years. Unfortunately, despite using the function data_dictionary and experimenting with various arguments (e.g., "population," "households," etc.), we were unable to retrieve population data. Instead, the package provided other types of data that were not relevant to our analysis.

@@

In comparison the third paper map looked as follows: ![Figure 4](data/paper3/original_plot.png)
